% !TEX program = xelatex

\documentclass{resume}
% \usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
% \usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{fontawesome5}

% \renewcommand{\baselinestretch}{1.1}
\hypersetup{hidelinks}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Lili Liang}

\basicInfo{
    (86) 175-4399-9485
    | \href{mailto:l2liang@cmu.edu}{l2liang@cmu.edu} 
    | \href{https://github.com/leungll}{\faGithub \ leungll} 
    | \href{https://www.linkedin.com/in/l2liang}{\faLinkedin \ l2liang}
    | \href{https://leungll.site/about}{\faHome \ leungll.site}
}

\section{Education}
\datedsubsection{\textbf{\href{https://www.cmu.edu}{Carnegie Mellon University}} (Incoming Student)}{Mountain View, CA} % todo 
\datedsubsection{Master's degree, Master of Science in Software Engineering}{08/2024 -- 12/2025}

\datedsubsection{\textbf{\href{https://en.nenu.edu.cn/}{Northeast Normal University}}}{Changchun, China}
\datedsubsection{Bachelor's degree, B.Eng. in Software Engineering}{09/2017 -- 06/2021}

\section{Technical Skills}
\textbf{Programming Languages:} Golang, Java, C/C++, SQL, Python, JavaScript, HTML/CSS, Markdown

\textbf{Frameworks:} RPC(Thrift), RocketMQ, Kafka, SpringBoot, MyBatis, Node.js, Zookeeper

\textbf{Databases:} MySQL, Redis, ElasticSearch, Hive, MongoDB

\textbf{Tools and Services:} Linux, Git, \LaTeX, Swagger, Google Cloud Platform, Amazon Web Services

\section{Work Experience}
\datedsubsection{\href{https://www.bytedance.com/en}{\textbf{ByteDance} (Parent company of TikTok)}}{Shenzhen, China}
\datedsubsection{\textit{Backend Software Engineer \textbf{Full-time}, TikTok E-commerce Fulfillment Group}}{07/2021 -- 10/2023}
\begin{itemize}[parsep=0.2ex]
    \item \textbf{Merchant Fulfillment}: \textit{Core developer}. Supported the construction of the multi-end capabilities for 
    merchant fulfillment and launched 23+ large and medium-sized projects. The business order volume has grown from 56k to 
    10 million.
    \item \textbf{OpenAPI}: \textit{Business owner}. Reviewed the historical architecture, tracked online issues, identified 
    and promptly addressed 16 historical bugs. Based on software development principles, took the lead in formulating interface 
    change specifications.
    \item \textbf{Stability Construction}: \textit{Business owner}. Completed the basic construction of business problem 
    troubleshooting tools, including the full-link tool reporting SDK, data cleaning, and full-scenario data dashboard, etc. 
    For online problem solving, it saved 75\% of human resources (21 people to 5 people).
    \item \textbf{Achievement}
      \begin{itemize}
          \item[$\circ$] \textbf{Annual performance appraisal: \textit{Exceed Expectation} and promoted} (top 1\%)
          \item[$\circ$] Global E-Commerce \textit{Spot Bonus} Award (Outstanding Job Performance, top 3\%)
      \end{itemize}
\end{itemize}

\section{Project Experience}
\datedsubsection{\textbf{Fulfillment Decision System and Configuration SDK Project} @ByteDance}{09/2022 -- 11/2022}
\datedsubsection{\textit{Project Owner. Technologies: Golang, KiteX, RocketMQ, SDK, RPC, Metrics, Grafana}}{}
\begin{itemize}[parsep=0.2ex]
    \item Implemented an action decision system that can encapsulate business decision logic, achieve configurability, 
    support grayscale release mechanism and exception rollback.
    \item Converted 25 business rules into rule expressions in the MVP version and designed a rule engine to complete 
    the logical calculation of the regular expression.
    \item Used the company's basic component TCC to configure rules, provide rule management, and read and write 
    capabilities. Completed the configuration management of business rules.
    \item Designed an action verification service based on the rule engine, which could offer two integration methods, 
    SDK and RPC, preventing single-point issues.
    \item \textbf{Result}: 3 months after being launched, access to SDK QPS: 1.1k, access to RPC QPS: 115 (B-side business).
\end{itemize}

\datedsubsection{\textbf{Fulfillment Oncall Tool Efficiency Improvement Project} @ByteDance}{12/2022 -- 03/2023}
\datedsubsection{\textit{Project Owner. Technologies: Golang, KiteX, SDK, ElasticSearch, Hive, RocketMQ, Metrics, Grafana}}{}
\begin{itemize}[parsep=0.2ex]
    \item Abstracted the key actions in each business, classified key actions according to e-commerce scenarios, and designed 
    common reporting business data for each key action.
    \item Designed a general business data reporting SDK for low-cost access to business services. Pushed the reported data 
    to ES via RocketMQ.
    \item Exported ES data to the data analysis platform through Hive for PM and operations to perform data analysis.
    \item \textbf{Result}: Based on the data reported by ES, SDE can quickly check the full-scenario data of the order based on the key ID. 
    For online problem solving, it saved 75\% of human resources (21 people to 5 people).
\end{itemize}

% \section{Research}
% \datedsubsection{\textbf{Solving Diversified Top-k Weight Clique Search Problem}}{07/2020 -- 09/2020}
% \datedsubsection{\textit{Research direction: algorithm solution}}{}
% \begin{itemize}
%     \item Proposed two encoding strategies for solving the diversified top-k weight clique search (DTKWCS) problem and two specific 
%     practical applications of DTKWCS. 
%     \item Conducted experiments to show that our encoding strategies are competitive, allowing to promote the applications of the 
%     DTKWCS problem, such as community detection, spectrum sharing, advertising placement, etc.
%     \item \textbf{Published} in JCR Q1 journal: 
%     \textbf{\href{https://link.springer.com/article/10.1007/s11432-020-3069-4}{\textit{Science China Information Sciences}}}.
% \end{itemize}

% \datedsubsection{\textbf{Research and Implementation of Community Friend Recommendation System Based on K-Plex}}{}
% \datedsubsection{\textit{Thesis Project \qquad Technologies: Vue. Js, SpringBoot, Redis, Shiro}}{12/2020 -- 04/2021}
% \begin{itemize}
%     \item Designed a heuristic search algorithm strategy for maximal enumeration of K-plex by improving the fast enumeration 
%     algorithm for large K-plex proposed by Conte et al. 
%     \item Conducted experiments to verify the effectiveness of the algorithm.
%     \item Achieved the architecture design and system implementation of the community friend recommendation system based on this 
%     algorithm model.
% \end{itemize}

% \section{Technical Blog}
% \begin{itemize}
%     \item \href{https://blog.csdn.net/liangllhahaha?type=blog}{[CSDN]}: output \textbf{60+} algorithm and engineering technical 
%     blogs, got \textbf{570,000+} views.

%     \item \href{https://github.com/leungll}{[GitHub]}：
%     \href{https://github.com/leungll/NENU-Courses}{\faGithub \ \textbf{NENU-Courses}} course guide open source project initiator.

%     \item \href{https://leungll.site/about}{[Personal Blog Site]}: Blog website built by myself.
%     \begin{itemize}
%       \item[$\circ$] Deployed the site in two lines; built CDN based on JsDelivr to optimize resource loading speed; 
%       applied site traffic analysis tools; implemented search engine inclusion (SEO).
%     \end{itemize}
% \end{itemize}

% \section{Awards and Honors}
% \begin{itemize}
%     \item \textit{Exceed Expectation} Performance Promotion, ByteDance (top 1\%) \hfill 2023
%     \item Global E-Commerce \textit{Spot Bonus} Award, ByteDance (Outstanding Job Performance, top 3\%) \hfill 2022
%     \item First Prize Scholarship, Outstanding Student Award, Practical Innovation Scholarship(top 7\%) \hfill 2021
%     \item \textit{Innovation Star} Award, NorthEast Normal University(top 3\%) \hfill 2020
%     \item President Scholarship, Outstanding Student Award (top 5\%) \hfill 2020
%     % \item C/C++ Programming Competition, University Group A, Jilin Division of the National Software 
%     % and Information Technology Talent Competition - Third Prize \hfill 2020
%     % \item Second Prize Scholarship, Outstanding Student Award \hfill 2019
%     \item First Prize and Team First Prize in the ``National University Green Computing Competition" (top 1\%) \hfill 2018
% \end{itemize}

% \section{Publications} % todo
% \begin{itemize}
%     \item Junping Zhou, Chumin Li, Yupeng Zhou, Mingyang Li, \textbf{Lili Liang}, and Jianan Wang, 
%     ``Solving diversified top-k weight clique search problem'', 
%     in \textbf{\href{https://link.springer.com/article/10.1007/s11432-020-3069-4}{\textit{Science China Information Sciences}}} 
%     and \textbf{\href{https://hsi-workshop.github.io/hsi2020-website/program.html}{\textit{HSI 2020(conjunction with IJCAI 2020)}}}, 
%     \href{https://hsi-workshop.github.io/hsi2020-website/hsi2020/Solving%20diversified%20top-k%20weight%20clique%20search%20problem%20with%20MaxSAT.pdf}{[PDF]}
% \end{itemize}

\end{document}
